Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-25 draft/chicago-spatial-covid-draft.tex
Updated ODE model figures

%images and image path
\usepackage{graphicx}
\graphicspath{ {./images/} }

@@

The next step is to identify the parameters at the ODE level.
To do this, we use a nonlinear optimization algorithm.
We determine the optimal parameters by minimizing the Euclidean distance between the time series generated by the model ($\num$) and the corresponding observed ($\obs$) time series,
\begin{equation}
	\N = \sum_i \left( \left| \log(C_\num (t_i)) - \log(C_\obs (t_i)) \right|^2 + \left| \log(R_\num (t_i)) - \log(R_\obs (t_i)) \right|^2 \right)
\end{equation}
where the index $i$ identifies a point in the time series.
The parameters are optimized to reproduce the reported total number of infected cases $C(t) = I(t) + R(t)$, and the total number of removed $R(t)$.

@@

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.

@@

>>>>

%images and image path
\usepackage{graphicx}
\usepackage{subfig}
\graphicspath{ {./images/} }

@@

The next step is to identify the parameters at the ODE level.
To do this, we use a nonlinear optimization algorithm.
We determine the optimal parameters by minimizing the Euclidean distance between the time series generated by the model ($\num$) and the corresponding observed ($\obs$) time series,
\begin{equation} \label{eq:obj}
	\N = \sum_i^{t_\text{fit}^\text{end}} \left( \left| \log(C_\num (t_i)) - \log(C_\obs (t_i)) \right|^2 + \left| \log(R_\num (t_i)) - \log(R_\obs (t_i)) \right|^2 \right)
\end{equation}
where the index $i$ identifies a point in the time series.
The parameters are optimized to reproduce the reported total number of infected cases $C(t) = I(t) + R(t)$, and the total number of removed $R(t)$.

@@

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.
The relevant results are given in Figure \ref{ode_results}.
We obtained the optimal ODE model parameters for Chicago from 1,000 optimizations that compared model predictions to jointly the number of cumulative infected and the deceases, as in Equation \ref{eq:obj}.

@@

\begin{figure}
	\centering
	\subfloat{\includegraphics[width=.475\textwidth]{ode_cases}}
	\subfloat{\includegraphics[width=.475\textwidth]{ode_deaths}} \\
	\subfloat{\includegraphics[width=.475\textwidth]{ode_IR}}
	\caption{ODE model for Chicago with fitting to official data from March 17, 2020 ($t = t_\text{init} = 1$) to September 30, 2020 ($t = t_\text{fit}^\text{end} = 198$).
		Left panel: Confirmed cases $C(t) = I(t) + R(t)$; Right panel: Number of deaths $D(t)$.
		Bottom panel shows the other populations: infected $I(t)$ and recovered $R(t)$.}
	\label{fig:ode_results}
\end{figure}
